|

### 2021-12-09 front-and-back-matter/99-appendices.Rmd
Fix broken cross-links
End of day:

## Chapter \@ref(background-heading) {#appendix-into}

@@

__Peer reviewed__

  * PRISMA main paper

  * PRISMA E&E

  * PRISMA 2020 software

  * COVID Suicide Living Review

  * Data extraction tools systematic review

<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->

__Under review/Preprints__

  * MSc Paper on systematic reviews of this thesis topic

  *

### Involvement of patients and the public {#appendix-ppi}

Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.

Additionally,

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}

### Code for publication rate analysis

```{r, eval=FALSE}
med_res <-
  # Use snapshot of published status from July 2021
  medrxivr::mx_search(
    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
    query = "*",
    from_date = "2019-07-01",
    to_date = "2019-08-01"
  ) %>%
  # Create indicator to show which records have been published
  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
  # Group by indicator variable and count
  group_by(pub_ind) %>%
  count()

## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}

### Deviations from protocol

<!-- TODO Complete -->

* MR tool, actually used Mamluk

* ROB-ME

* No MCI, given size of dementia findings

* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered separate things here.[@sterne2013]

 * Dose response

### Web of Science Databases Searched {#appendix-wos-databases}

(ref:wosDatabases-caption) Summary of Web of Science databases searched.

@@

(ref:searchHits-caption) Overview of the full Medline search strategy.

(ref:searchHits-scaption) searchHits

```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
```

@@

@@

mx_data <- mx_api_content(to_date = "2019-07-01")

bx_data <- mx_api_content(server = "biorxiv",
                                    to_date = "2019-07-01")

topic1 <- c(mx_caps("statin"),
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            mx_caps("triglycer"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            mx_caps("ezetim"),
            mx_caps("fibrate"),
            mx_caps("bile acid"),
            mx_caps("lipoprotein"),
            mx_caps("lipid"),
            mx_caps("cholesterol"))

topic2 <- c(mx_caps("dementia"),
            mx_caps("alzheim"),
            mx_caps("MCI"),
            mx_caps("mild cognitive"))

query <- list(
  topic1,
  topic2
)

bx_results <- mx_search(bx_data, query)

mx_results <- mx_search(mx_data, query)

@@

Note

@@

Gwet's AC1 is defined as:

$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$

@@

### MR risk of bias tool {#appendix-mr-rob}

@@

## Chapter \@ref(sys-rev-results-heading)

@@

@@

```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
```

@@

```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
```

## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}

@@

## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}

@@

@@

@@

## Chapter \@ref(tri-heading) {#appendix-tri-analysis}

### Calculation of average adjustment from expert elicitation {#appendix-adjustment-values}

### Code lists

@@

@@

## Chapter \@ref(discussion-heading)

@@

@@

- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))

@@

This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

@@

<!-- TODO Need to complete this sections -->

_TBC_

@@

The following pages contain copies of papers arising from work performed as part of this thesis.

@@

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

>>>>

## Chapter 1 {#appendix-into}

@@

In addition to publications arising directly from this thesis (described in Section \@ref(literature-contributions) & included in Appendix \@ref(published-papers)), I have been involved in a number of external research projects. Taken together, these additional projects provided extensive experience in evidence synthesis methods and in collaborating across large teams.

During 2020, I was involved in the updating of the Preferred Reporting Items for Systematic reviews and Meta-Analyses (PRISMA) statement. My contributions were focused on the data sharing aspects of the guidelines and on building an interactive web application that would allow users to complete the PRISMA checklist. Publications arising from this work are listed below:

*	*Page, M.J., Moher, D., Bossuyt, P., Boutron, I., Hoffmann, T., Mulrow, C., Shamseer, L., Tetzlaff, J., Akl, E., Brennan, S.E., Chou, R., Glanville, J., Grimshaw, J., Hróbjartsson, A., Lalu, M.M., Li, T., Loder, E., Mayo-Wilson, E., McDonald, S., __McGuinness, L.A.__, Stewart, L., Thomas, J., Tricco, A., Welch, V.A., Whiting, P., McKenzie, J. (2021). PRISMA 2020 statement: updated guidelines for reporting systematic reviews and meta-analyses. BMJ 372:n71 [10.1136/bmj.n71](https://doi.org/10.1136/bmj.n71)*

*	*Page, M.J., Moher, D., Bossuyt, P., Boutron, I., Hoffmann, T., Mulrow, C., Shamseer, L., Tetzlaff, J., Akl, E., Brennan, S.E., Chou, R., Glanville, J., Grimshaw, J., Hróbjartsson, A., Lalu, M.M., Li, T., Loder, E., Mayo-Wilson, E., McDonald, S., __McGuinness, L.A.__, Stewart, L., Thomas, J., Tricco, A., Welch, V.A., Whiting, P., McKenzie, J. (2021). PRISMA 2020 explanation and elaboration: updated guidance and exemplars for reporting systematic reviews. BMJ 372:n160. DOI: [10.1136/bmj.n160](https://doi.org/10.1136/bmj.n160)*

* *Haddaway, N. R., Page, M. J., Pritchard, C. C., & McGuinness, L. A. (2021). PRISMA2020: An R package and Shiny app for producing PRISMA 2020-compliant flow diagrams, with interactivity for optimised digital transparency and Open Synthesis. MedRxiv, DOI: [10.1101/2021.07.14.21260492](https://doi.org/10.1101/2021.07.14.21260492)*

&nbsp;

In response to the COVID-19 pandemic, I worked with a team of evidence synthesists to develop a literature searching/screening pipeline. This work underpinned a living systematic review on impact of the COVID-19 pandemic on self-harm and suicidal behaviour. Subsequently, the pipeline enabled rapid reviews of related topics, such as an analysis of the available evidence by population.

*	*John, A., Okolie, C., Eyles, E., Webb, R.T., Schmidt, L., __McGuinness, L.A.__, Olorisade, B.K., Arensman, E., Hawton, K., Kapur, N. and Moran, P., 2020. The impact of the COVID-19 pandemic on self-harm and suicidal behaviour: a living systematic review. F1000Research, 9(1097). DOI: &nbsp; [10.12688/f1000research.25522.2](https://doi.org/10.12688/f1000research.25522.2)*

*	*John, A., Eyles, E., __McGuinness, L.A.__, Okolie, C., Olorisade, B.K., Schmidt, L., Webb, R.T., Arensman, E., Hawton, K., Kapur, N. and Moran, P., 2020. The impact of the COVID-19 pandemic on self-harm and suicidal behaviour: protocol for a living systematic review. F1000Research, 9(644), p.644. DOI: [10.12688/f1000research.24274.1](https://doi.org/10.12688/f1000research.24274.1)*

* *Eyles, E., Moran, P., Okolie, C., Dekel, D., Macleod-Hall, C., Webb, R. T., Schmidt, L., Knipe, D., Sinyor, M., __McGuinness, L. A.__, Arensman, E., Hawton, K., O’Connor, R. C., Kapur, N., O’Neill, S., Olorisade, B., Cheng, H.-Y., Higgins, J. P. T., John, A., & Gunnell, D. (2021). Systematic review of the impact of the COVID-19 pandemic on suicidal behaviour amongst health and social care workers across the world. Journal of Affective Disorders Reports, 6, 100271. DOI: [10.1016/j.jadr.2021.100271](https://doi.org/10.1016/j.jadr.2021.100271)*

&nbsp;

Finally, I have acted as part of a large review team for a number of other evidence synthesis exercises:

*	*Grant, M. C., Geoghegan, L., Arbyn, M., Mohammed, Z., __McGuinness, L.A.__, Clarke, E. L., & Wade, R. (2020). The Prevalence of Symptoms in 24,410 Adults Infected by the Novel Coronavirus (SARS-CoV-2; COVID-19): A Systematic Review and Meta-Analysis of 148 Studies from 9 Countries. PLOS ONE. DOI: [10.1371/journal.pone.0234765](https://doi.org/10.1371/journal.pone.0234765)*

* *Cheng, H.Y., __McGuinness, L.A.__, Elbers, R.G., MacArthur, G.J., Taylor, A., McAleenan, A., Dawson, S., López-López, J.A., Higgins, J.P., Cowlishaw, S. and Lingford-Hughes, A. (2020). Treatment interventions to maintain abstinence from alcohol in primary care: systematic review and network meta-analysis. BMJ, 371. DOI: [10.1136/bmj.m3934](https://doi.org/10.1136/bmj.m3934)*

*	*Schmidt, L., Olorisade, B.K., __McGuinness, L.A.__, Thomas, J. and Higgins, J.P. (2020). Data extraction methods for systematic review (semi) automation. F1000Research, 10:401. DOI: &nbsp; [10.12688/f1000research.51117.1](https://doi.org/10.12688/f1000research.51117.1)*

## Chapter 2 {#appendix-sys-rev-tools}

### Code for publication rate analysis {#appendix-tools-pub}

medRxiv automatically links preprints to their published counterparts, and provides the DOI of the published article as part of the metadata on a given preprint. Using `medrxivr` to access this data, I could assess the two-year publication rate of preprints originally posted to medRxiv in July 2019. The code used for this analysis is presented below:

&nbsp;

```{r, eval=FALSE}
# Load relevant packages
library(medrxivr)
library(dplyr)

# Use snapshot of published status from July 2021
  mx_search(
    mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
    query = "*",
    # Limit to those 129 records published in July 2019
    from_date = "2019-07-01",
    to_date = "2019-08-01"
  ) %>%

# Create indicator to show which records have been published
  mutate(Status = ifelse(published == "NA",
                          "Not published",
                          "Published")) %>%

# Group by indicator variable ("Published"/"Not published")
  group_by(Status) %>%

# Get total number per group, and percentage of total (N=129)
  summarise(N = n(),
            Percent = comma(n() / 129 * 100)) 
```

&nbsp;

As shown in Table \@ref(tab:medRes-table), two-thirds of preprints were published within two years of their submission to medRxiv.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:medRes-caption) Publication status of medRxiv preprints deposited in July 2019, allowing for a two-year lag

(ref:medRes-scaption) Publication status of medRxiv preprints

```{r medRes-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

## Chapter 3 {#appendix-sys-rev}

### Deviations from protocol {#appendix-sys-rev-deviations}

There were a number of deviations from the pre-registered protocol for the systematic review reported in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading):[@mcguinnessluke2020]

* I had originally intended to examine both dementia and mild cognitive impairment (MCI) as outcomes of interest. However, given the large number of relevant records for the dementia outcomes, I did not include MCI as an outcome.

* For Mendelian randomisation analyses, I had originally intended to use a panel of experts to assess he risk of bias in this study design. However, through private correspondence with the authors of a review of risk-of-bias assessment tools for Mendelian randomisation studies (since published[@spiga2021]), I became aware of the Mamluk _et al_ tool. Given this tool was considered to be the best available for assessing Mendelian randomisation studies and that it followed a domain-based approach, enabling comparison with tools for other study designs, I decided to use it in the review.

* I performed an additional assessment of the risk of bias due to missing evidence using the ROB-ME tool. This analysis was not planned because the tool did not exist when the protocol was written.

* I had originally intended to assess sources of funding alongside bias. However, on further reading,[@sterne2013] I learned that any bias introduced by sources of funding would operate through one of the existing domains of the risk-of-bias tools. As such, I did not consider funding sources seperately.

 * Finally, I performed a dose response meta-analysis to assess the evidence for a non-linear realtionship between lipids and dementia outcomes. This marked a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.

### Web of Science databases searched {#appendix-wos-databases}

(ref:wosDatabases-caption) Summary of Web of Science databases searched. The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.

@@

An overview of the number of hits per database, in addition to the full line-by-line search results for the each database, are presented below.

(ref:searchOverviewAppendix-caption) Summary of number of records identified in each database searched

(ref:searchOverviewAppendix-scaption) searchOverviewAppendix

```{r searchOverviewAppendix-table, message=FALSE, results="asis", echo = FALSE}
```

(ref:searchHitsMedline-caption) Overview of the full Medline search strategy.

(ref:searchHitsMedline-scaption) Medline search strategy

```{r searchHitsMedline-table, message=FALSE, results="asis", echo = FALSE}
```

&nbsp;

(ref:searchHitsEmbase-caption) Overview of the full Embase search strategy.

(ref:searchHitsEmbase-scaption) Embase search strategy

```{r searchHitsEmbase-table, message=FALSE, results="asis", echo = FALSE}
```

&nbsp;

(ref:searchHitsPI-caption) Overview of the full PyscINFO search strategy.

(ref:searchHitsPI-scaption) PyscINFO search strategy

```{r searchHitsPI-table, message=FALSE, results="asis", echo = FALSE}
```

&nbsp;

(ref:searchHitsCentral-caption) Overview of the full CENTRAL search strategy.

(ref:searchHitsCentral-scaption) CENTRAL search strategy

```{r searchHitsCentral-table, message=FALSE, results="asis", echo = FALSE}
```

&nbsp;

(ref:searchHitsWos-caption) Overview of the full Web of Science search strategy.

(ref:searchHitsWos-scaption) Web of Science search strategy

```{r searchHitsWos-table, message=FALSE, results="asis", echo = FALSE}
```

@@

As detailed extensively in the main text, the inclusion of preprinted literature was a key aspect of the review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading). Using the `medrxivr` tool presented in Chapter \@ref(sys-rev-tools-heading).

Given the relatively small number of records contained in the preprint server, no study design filters were employed. For the same reason, the number of search terms is smaller compared with the main database searches, as terms returning no records have been removed.

@@

# Define exposure search terms
topic1 <- c(mx_caps("statin"),
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            mx_caps("triglycer"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            mx_caps("ezetim"),
            mx_caps("fibrate"),
            mx_caps("bile acid"),
            mx_caps("lipoprotein"),
            mx_caps("lipid"),
            mx_caps("cholesterol"))

# Define outcome search terms
topic2 <- c(mx_caps("dementia"),
            mx_caps("alzheim"),
            mx_caps("MCI"),
            mx_caps("mild cognitive"))

# Combine search topics using Boolean AND
query <- list(topic1, topic2)

# Run search in bioRxiv
bx_data <- mx_api_content(server = "biorxiv",
                          to_date = "2019-08-01")
bx_results <- mx_search(bx_data, query)

# Run search in medRxiv
mx_data <- mx_api_content(server = "medrxiv",
                          to_date = "2019-08-01")
mx_results <- mx_search(mx_data, query)

@@

@@

Gwet's agreement coefficient, $AC1$ is defined as:

\begin{equation}
AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}
  (\#eq:AC1-words)
\end{equation}

@@

### Risk-of-bias assessment tool for Mendelian randomisation studies {#appendix-mr-rob}

@@

## Chapter 4

@@

In addition to examining a non-linear relationship between LDL-c and Alzheimer's disease (see Figure \@ref(fig:lipidsDoseResponse)), I performed a dose response analysis for two other exposure-outcome pairs. The results of these analyses are presented below.

@@

```{r drDemeniaTC, echo = FALSE, results="asis", fig.align='center', fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='60%', fig.scap='(ref:drDemeniaTC-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
```

@@

```{r drAdLDL, echo = FALSE, results="asis", fig.align='center', fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='60%', fig.scap='(ref:drAdLDL-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
```

## Chapter 5 {#appendix-cprd-analysis}

@@

Any changes made to the approved protocol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".

Changes include:

-   Use of a time-varying treatment indicator, to correctly classify time-at-risk.
-   Inclusion of additional covariates that are adjusted for in the main model.

## Chapter 6 {#appendix-ipd-analysis}

@@

__To be copied from email__

@@

&nbsp;

<!----------------------------------------------------------------------------->
(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis

(ref:ipdDementiaDef-scaption) Definition of dementia outcomes in IPD meta-analysis

```{r ipdDementiaDef-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

@@

## Chapter 7 {#appendix-tri-analysis}

### Calculation of average adjustment values from previous expert elicitation exercise {#appendix-adjustment-values}

The paper describing the bias/indirectness-adjusted meta-analysis method used expert elicitation to define a distribution for  bias and indirectness across eight studies examining the effectiveness of routine anti-D prophylaxis in Rhesus negative women.[@turner2009] The authors consider five sources of bias (selection bias, performance bias, attrition bias, detection bias and other bias) and four sources of indirectness (population, intervention, control, outcome). For each domain of bias/indirectness, four experts were asked to define the 67% interval around the effect expected due to bias/indirectness in the absence of a true effect. Additive or multiplicative scales were used to capture the intervals for additive and proportional bias/indirectness, respectively. The authors then use assumed log-normality of these distributions to derive a mean and variance for each on the log scale.

In an attempt to inform the prior distributions used in the triangulation exercise presented in Chapter \@ref(tri-heading), I first averaged the mean and variance values across the four experts for each source of bias/indirectness within each study. I averaged the absolute value of the mean, as I wanted to obtain the average adjustment regardless of direction of adjustment which was indicated using the sign of the mean in the original analysis).

I then took the average and maximum of these averaged mean and variance values. The distributions arising from this analysis are presented in Table \@ref(tab:turnerEstimates-table). The two step approach (averaging across assessors before taking the average/maximum across sources of bias) was important. While the final mean values will be the same whichever approach is taken, in a one-step process the maximum value can be artificially inflated by a single expert's estimate. Averaging across experts for a given bias in a given study before taking the maximum value across biases and studies prevented this.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009]

(ref:turnerEstimates-scaption) turnerEstimates

```{r turnerEstimates-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

The mean values shown were used to define the distributions assigned to  "Moderate" bias/indirectness judgements in my analysis (see Tables \@ref(tab:priorsAdd-table) & \@ref(tab:priorsIndirect-table)).

@@

As discussed in the main text, I defined two sets of additive bias distributions as a sensitivity analysis. The results for the two case studies under the two scenarios are presented in the figures below.

@@

## Chapter 8

@@

All software projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

@@

- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-analysis-heading))

@@

This thesis was written in RMarkdown using the RStudio integrated development environment. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")` The version number of these packages is shown below:

&nbsp;

```{r, echo = FALSE}
sessionInfo()
```

@@

<!-- TODO Need to complete this sections -->
The robvis package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.

robvis currently contains templates for the following tools:

* ROB2
* ROBINS-I
* QUADAS-2
* ROB1

For the direction bias plots, the data expected by the tools is more comprehensive.

&nbsp;

\blandscape
<!----------------------------------------------------------------------------->
(ref:biasData-caption) biasData

(ref:biasData-scaption) biasData

```{r biasData-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

<!----------------------------------------------------------------------------->
(ref:biasDirectionData-caption) biasDirectionData

(ref:biasDirectionData-scaption) biasDirectionData

```{r biasDirectionData-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
\elandscape

@@

The following pages contain copies of the following publications:

- _**McGuinness L. A.**, Higgins J. P. T., Walker, V. M., Davies, N. M., Martin, R. M., Coulthard, E., Davey-Smith, G., Kehoe, P. G., and Ben-Shlomo, Y. (2021) Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the Clinical Practice Research Datalink. medRxiv. DOI:   [10.1101/2021.10.21.21265131](https://doi.org/10.1101/2021.10.21.21265131)_

- _**McGuinness, L. A.**, and L Schmidt. (2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R. Journal of Open Source Software 5.54 2651. DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_

- _**McGuinness, L. A.**, and Higgins J. P. T. (2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method). DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_

- _**McGuinness, L. A.**, and Sheppard A. L. 2020. “A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887. DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_

- _Hennessy, E. A., Acabchuk, R., Arnold, P. A., Dunn, A. G., Foo, Y. Z., Johnson, B. T., Geange, S. R., Haddaway, N. R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A. Welch, V.,  **and McGuinness L. A.** (2021). Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact. Prevention Science . DOI: [10.1007/s11121-021-01279-8](https://doi.org/10.1007/s11121-021-01279-8)_

These manuscripts arose from work performed as part of this thesis, as discussed more fully in Section \@ref(literature-contributions).

@@

<!-- TODO These have been removed so as to not mess-up the plagarism score -->

\includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

### 2021-12-09 front-and-back-matter/_acknowledgements.Rmd
End of day:

Additionally, I would like to thank Sharen O’Keefe.

There are so many people without whom this would not have been possible:

[**Check all name spellings**]

Sharen O'Keffe
Neal Haddaway
Martin Westgate

robvis contributors: (there are at least 3)

Annual reviewers: Rupert Payne and Emma Anderson

Those who contributed their time to dual marking papers and code with me,

I am a NIHR Doctoral Research Fellow with grant code **TBC**. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.

Statistical support: check emails!

All authors who volunteered time and effort to provided

A special thanks goes out to Mark Newbury of the

Finally, thanks to parents and Ciara Gardiner.

\begin{flushright}
Canynge Hall, Bristol \\
1 December 2021
\end{flushright}

>>>>

There are many people without whose input and support this work would have been severely diminised:

First and foremost, I would like to thank my supervisors - Julian Higgins, Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their support over the past three years. Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews. Sharen O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support. Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.

Thanks must also go to those who contributed their time and energy to my research projects: Matthew Lee, Lena Schmidt, Alexandra McAleenan, and Vincent Cheng. Francesca Spiga kindly shared an advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner shared her code for bias-/indirectness-adjusted meta-analyses that underpins the quantitative triangulation framework presented in Chapter \@ref(tri-heading). Thanks to Vivienne for proof-reading.

A particular thank you to Emily Hennessy, with whom I co-wrote the guidance paper for preparing primary research for incorporation into systematic reviews. Similarly, thanks to Athena Sheppard for her support in assessing the impact of journal polices on open-data sharing.

Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
<<github>>. A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.

I have been supported throughout my studies by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048). The views expressed in this thesis are my own and do not necessarily represent those of the NIHR or the Department of Health and Social Care.

On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times. Thanks to Mum and Dad for your never-ending love and support (I promise I'll get a real job now!). Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.

Finally, deepest thanks to Ciara Gardiner: holder-of-forts, maker-of-spreadsheets, and all-round fiancee-extraordinaire. I can't wait for the next adventure with you.

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

\begin{flushright}
Canynge Hall, Bristol \\\
1 December 2021
\end{flushright}

### 2021-12-09 front-and-back-matter/abbreviations.tex
Double-saving
End of day: -700
End of day: 0
End of day: 2490
End of day:

% do not edit by hand - add to abbreviations.csv instead
% First parameter can be changed eg to "Glossary" or something.
% Second parameter is the max length of bold terms.
\begin{mclistof}{List of Abbreviations}{3.2cm}
\item[DOI] Digitial object identifier
\item[HDL] High Density Lipoprotein
\item[MR] Mendelian randomization
\end{mclistof}

>>>>

% do not edit by hand - add to abbreviations.csv instead
% First parameter can be changed eg to "Glossary" or something.
% Second parameter is the max length of bold terms.
\begin{mclistof}{List of Abbreviations}{3.2cm}
\item[AC] Agreement coefficient
\item[ACE] Acetylcholinesterase
\item[AD] Alzheimer's disease
\item[ADGC] Alzheimer’s Disease Genetics Consortium
\item[API] Application programming interface
\item[ApoE] Apolipoprotein E
\item[BAS] Bile acid sequestrants
\item[BMI] Body mass index
\item[CAD] Coronary arterial disease
\item[CaPS]  Caerphilly Prospective Study
\item[CBS] Coronary bypass surgery
\item[CCI] Charlson co-morbidity index
\item[CIND] Cognitive impairment not dementia
\item[CKD] Chronic kidney disease
\item[CPRD] Clinical Practice Research Datalink
\item[CRAN] Comprehensive R Archive Network
\item[CSV] Comma separated value
\item[CVD] Cardiovascular disease
\item[DOI] Digitial object identifier
\item[DPUK] Dementia Platform UK
\item[DSM] Diagnostic and Statistical Manual of Mental Disorders
\item[EHR] Electronic health record
\item[EPIC] European Prospective Investigation of Cancer 
\item[FAGs] Fatty acid groups
\item[GLGC] Global Lipids Genetic Consortium
\item[GWAS]  Genome wide association studies
\item[HDL] High density dipoprotein
\item[HES] Hospital episode statistics
\item[HMG-CoA] 3-hydroxy-3-methylglutaryl-coenzyme-A
\item[HMGCR] HMG-CoA reductase
\item[HR] Hazard ratio
\item[ICD] International Classification of Diseases
\item[IGAP] International Genomics of Alzheimer's Project
\item[IHD]  Ischemic heart disease
\item[IMD] Index of multiple deprivation
\item[IPD] Individual participant data
\item[IV] Instrumental variable
\item[JUPITER] Justification for the Use of Statin in Prevention: An Intervention Trial Evaluating Rosuvastatin
\item[LDL-c] Low density lipoprotein cholesterol
\item[LRA] Lipid regulating agent
\item[MCI] Mild cognitive impairment
\item[MICE] Multiple imputation by chained equations
\item[MMSE] Mini Mental State Exam
\item[MoCA] Montreal Cognitive Assessement
\item[MR] Mendelian randomization
\item[NAG] Nicotinic acid groups
\item[NINDS-ADRA] National Institute of Neurological Disorders and Stroke - Alzheimer's Disease and Related Disorders Association
\item[NINDS-AIREN] National Institute of Neurological Disorders and Stroke - Association Internationale pour la Recherche en l'Enseignement en Neurosciences
\item[NOS] Newcastle-Ottowa Scale
\item[NRSE] Non-randomised studies of exposures
\item[NRSI] Non-randomised studies of interventions
\item[OR] Odds ratio
\item[PAD] Peripheral arterial disease
\item[PCSK9i] PCSK9 inhibitors
\item[PDF] Portable document format
\item[PR] Proportional hazards
\item[PROSPER] Prospective Study of Pravastatin in the Elderly
\item[PYAR] Participant-years-at-risk
\item[RCT] Randomised controlled trial
\item[REML] Restricted maximum likelihood 
\item[RoB-ME] Risk of bias due to missing evidence
\item[RR] Risk/rate ratio
\item[SD] Standard deviation
\item[SNP] Single nucleotide polymorphism
\item[TC] Total cholesterol
\item[TG] Triglycerides
\item[VaD] Vascular dementia
\end{mclistof}
